\TheTitle

### 2017-07-13 paper/study.tex
Fixing study parts (part 2)
Oh that was painful to type.

\begin{table}[htpb]
  \centering
  \caption{Summarization Correctness Results}
  \label{tab:correctness_table}
  \begin{tabular}{crrc}
    \toprule
    Task                & $\chi^2$ & $p$-value & Conclusion\\\midrule
    T4                  & 13.07    & 0.0003    & Reject $H_0$\\
    \multirow{2}{*}{T5} & 5.14     & 0.0233    & Reject $H_0$\\
                        & 5.14     & 0.0233    & Reject $H_0$\\
    T6                  & 14.06    & 0.0002    & Reject $H_0$\\
    T7                  & 11.07    & 0.0009    & Reject $H_0$\\
    T8                  & 13.07    & 0.0003    & Reject $H_0$\\
    \multirow{2}{*}{T9} & 4.17     & 0.0412    & Reject $H_0$\\
                        & 6.13     & 0.0133    & Reject $H_0$\\
    T10                 & 4.00     & 0.0455    & Reject $H_0$\\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{itemize}
  \item

    T4; The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
      & Incorrect & 15                           & 2\\
    \end{tabular}
    \vspace{3mm}

  \item

    T5; The correctness results are split for this task. For \comA, the
    $\chi^2$ statistic is $5.14$ with a $p-value$ of $0.02334$. $5.14 >
    3.841$ and $0.02334 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 4                            & 0\\
                             & Incorrect & 7                            & 0\\
    \end{tabular}
    \vspace{3mm}

@@

  \item

    T6; The $\chi^2$ statistic is $14.06$ with a p-value of $0.0002$.
    $14.06 > 3.841$ and $0.0002 < 0.05$, therefore we reject the null
    hypothesis.

    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 5                            & 0\\
      & Incorrect & 16                           & 2\\
    \end{tabular}

  \item

    T7; The $\chi^2$ statistic is $11.07$ with a p-value of $0.0009$.
    $11.07 > 3.841$ and $0.0009 < 0.05$, therefore we reject the null
    hypothesis.

    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 8                            & 0\\
      & Incorrect & 13                           & 2\\
    \end{tabular}\\

  \item

    T8; The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.

    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
      & Incorrect & 15                           & 2\\
    \end{tabular}\\

  \item

    T9; The correctness results are split for this task. For \comA, the
    $\chi^2$ statistic is $4.17$ with a p-value of $0.0412$. $4.17 >
    3.841$ and $0.0412 < 0.05$, therefore we reject the null hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 5                            & 0\\
                             & Incorrect & 6                            & 0\\
    \end{tabular}
    \vspace{3mm}

@@

  \item

    T10; The $\chi^2$ statistic is $4$ with a p-value of $0.0455$.
    $4 > 3.841$ and $0.0455 < 0.05$, therefore we reject the null
    hypothesis. The p-value is very close to the $\alpha$ value in this
    case, so the conclusion is not as well defined.

    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}   & Correct   & 14                           & 1\\
      & Incorrect & 8                            & 0\\
    \end{tabular}

@@

>>>>

\begin{table*}[htpb]
  \centering
  \caption{Summarized Correctness, Accuracy, and Timing results for the summarization tasks}
  \label{tab:summarization_table}
  \begin{tabular}{ccc}
    % Correctness
    \begin{tabular}{crrc}
      \toprule
      Task                  & $\chi^2$ & $p$-value  & Conclusion\\\midrule
      T4                    & 13.07    & 0.0003     & Reject $H_0$\\
      \multirow{2}{*}{T5}   & 5.14     & 0.0233     & Reject $H_0$\\
                            & 5.14     & 0.0233     & Reject $H_0$\\
      T6                    & 14.06    & 0.0002     & Reject $H_0$\\
      T7                    & 11.07    & 0.0009     & Reject $H_0$\\
      T8                    & 13.07    & 0.0003     & Reject $H_0$\\
      \multirow{2}{*}{T9}   & 4.17     & 0.0412     & Reject $H_0$\\
                            & 6.13     & 0.0133     & Reject $H_0$\\
      T10                   & 4.00     & 0.0455     & Reject $H_0$\\
      \bottomrule
    \end{tabular}
    &

    % Accuracy
    \begin{tabular}{clrc}
      \toprule
      Task & $p$-value            & Delta Est. & Conclusion\\\midrule
      T4   & $7.8 \times 10^{-5}$ & -0.61      & Reject $H_0$\\
      T5   & $7.2 \times 10^{-5}$ & -0.63      & Reject $H_0$\\
      T6   & $1.2 \times 10^{-5}$ & -0.69      & Reject $H_0$\\
      T8   & $5.8 \times 10^{-4}$ & -0.54      & Reject $H_0$\\
      T9   & $0.009$              & -0.42      & Reject $H_0$\\
      T10  & $0.002$              & -0.35      & Reject $H_0$\\
      \bottomrule
    \end{tabular}
    &
    % Timing
    \begin{tabular}{clrc}
      \toprule
      Task                 & $p$-value & Delta Est. & Conclusion\\\midrule
      T4                   & 0.0007    & -0.58      & Reject $H_0$\\
      T5                   & 0.0142    & -0.42      & Reject $H_0$\\
      T6                   & 0.0168    & -0.41      & Reject $H_0$\\
      \multirow{2}{*}{T7}  & 0.2586    & -0.29      & Do not reject $H_0$\\
                           & 0.0780    & -0.43      & Do not reject $H_0$\\
      T8                   & 0.0009    & -0.57      & Reject $H_0$\\
      T9                   & 0.0002    & -0.63      & Reject $H_0$\\
      T10                  & 0.0001    & -0.66      & Reject $H_0$\\
      \bottomrule
    \end{tabular}
  \end{tabular}
\end{table*}

@@

\begin{itemize}
  \item T4

    \textbf{Correctness:}
    The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                            &           & \multicolumn{2}{c}{Linvis}\\
                            &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
                            & Incorrect & 15                           & 2\\
    \end{tabular}
    \vspace{3mm}

    \tool improves the correctness when determine the series of merges
    involved with merging a commit.

    \textbf{Accuracy:} The p-value is $7.8 \times 10^{-5}$, which is
    less than 0.05; therefore we reject the null hypothesis. The Delta
    estimate is -0.61, which indicates a large effect size. \tool
    improves accuracy when determining the series of merges involved
    with merging a commit.

    \textbf{Timing:}
    The p-value is $0.0007$, which is less than 0.05; therefore we
    reject the null hypothesis. The delta estimate is -0.58, which
    indicates a large effect size. \tool decreases the time taken to
    determine the series of merges involved with merging a commit.

    Overall, \tool is able to help users determine the series of merges
    that a commit takes more quickly and more accurately than Gitk.

  \item T5

    \textbf{Correctness:}
    The correctness results are split for this task. For \comA, the
    $\chi^2$ statistic is $5.14$ with a $p-value$ of $0.02334$. $5.14 >
    3.841$ and $0.02334 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 4                            & 0\\
                             & Incorrect & 7                            & 0\\
    \end{tabular}
    \vspace{3mm}

@@

    While there is a difference in correctness between different-sized
    merge-trees, \tool improves correctness of determining the other
    commits related to a commit in trees of varying sizes.

    \textbf{Accuracy:}
    The p-value is $7.2 \times 10^{-5}$, which is less than 0.05;
    therefore we reject the null hypothesis. The Delta estimate is
    -0.63, which indicates a large effect size. \tool improves
    accuracy when determining other commits related to a commit.

    \textbf{Timing:}
    The p-value is $0.0142$, which is less than 0.05; therefore we
    reject the null hypothesis. The delta estimate is -0.58, which
    indicates a large effect size. \tool decreases the time taken to
    determine other commits related to a commit.

    Overall, \tool helps users determine other commits that are merged
    with another commit more quickly and more accurately.

  \item T6

    \textbf{Correctness:}
    The $\chi^2$ statistic is $14.06$ with a p-value of $0.0002$.
    $14.06 > 3.841$ and $0.0002 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 5                            & 0\\
      & Incorrect & 16                           & 2\\
    \end{tabular}
    \vspace{3mm}

    \tool improves correctness when determining how many authors are
    involved with a merge.

    \textbf{Accuracy:} The p-value is $1.2 \times 10^{-5}$, which is
    less than 0.05; we reject the null hypothesis. The delta estimate is
    -0.69, which indicates a large effect size. \tool improves accuracy
    when determining how many authors are involved with a merge.

    \textbf{Timing:} The p-value is 0.0168, which is less that 0.05; we
    reject the null hypothesis. The delta estimate is -0.41, which
    indicates a medium effect size. \tool decreases the time taken to
    determine the number of authors involved in a commit.

    Overall, \tool assists users with determining the number of authors
    involved in a merge more quickly and more accurately.

  \item T7

    \textbf{Correctness:}
    The $\chi^2$ statistic is $11.07$ with a p-value of $0.0009$.
    $11.07 > 3.841$ and $0.0009 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 8                            & 0\\
      & Incorrect & 13                           & 2\\
    \end{tabular}\\
    \vspace{3mm}

    \tool improves the correctness of participants when determining the
    author that contributed the most changes to a merge.

    \textbf{Timing:} The null hypothesis is not rejected in the case of
    \comA, but is rejected in the case of \comB. This indicates that
    \tool is able to help users determine who made the most
    contributions to a merge in a large tree than in a small tree.

    Overall, \tool improves the correctness for trees of various sizes,
    but only has an effect on the amount of time taken when the tree is
    large.

  \item T8

    \textbf{Correctness:}
    The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
      & Incorrect & 15                           & 2\\
    \end{tabular}\\
    \vspace{3mm}

    \textbf{Accuracy:} The p-value is $5.8 \times 10^{-4}$, which is
    less than 0.05; we reject the null hypothesis. The delta estimate is
    -0.54, indicating a large effect size. \tool improves accuracy when
    determining how many files were modified at a merge.

    \textbf{Timing:} The p-value is 0.0009, which is less than 0.05; we
    reject the null hypothesis. The delta estimate is -0.57, indicating
    a large effect size.

  \item T9

    \textbf{Correctness:}
    The correctness results are split for this task. For \comA, the
    $\chi^2$ statistic is $4.17$ with a p-value of $0.0412$. $4.17 >
    3.841$ and $0.0412 < 0.05$, therefore we reject the null hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 5                            & 0\\
                             & Incorrect & 6                            & 0\\
    \end{tabular}
    \vspace{3mm}

@@

    \textbf{Accuracy:} The p-value is $0.009$, which is less than
    $0.05$; we reject the null hypothesis. The delta estimate is -0.42,
    indicating a medium effect size. \tool improves accuracy when
    determining which file had the most changes.

    \textbf{Timing:} We reject the null hypothesis; the delta estimate
    is -0.63, indicating a large effect size. \tool decreases the time
    taken to determine which file had the most changes.

    Overall, \tool is able to assist users determine which file had the
    most changes more quickly and accurately.

  \item T10

    \textbf{Correctness:}
    The $\chi^2$ statistic is $4$ with a p-value of $0.0455$.
    $4 > 3.841$ and $0.0455 < 0.05$, therefore we reject the null
    hypothesis. The p-value is very close to the $\alpha$ value in this
    case, so the conclusion is not as well defined.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}   & Correct   & 14                           & 1\\
      & Incorrect & 8                            & 0\\
    \end{tabular}
    \vspace{3mm}

    \textbf{Accuracy:} The null hypothesis is rejected; the delta
    estimate is -0.35, indicating a medium effect size. \tool provides
    an improvement in accuracy when determining which modules are
    involved with a merge.

    \textbf{Timing:} The null hypothesis is rejected; the delta estimate
    is -0.66, indicating a large effect size. \tool decreases the time
    taken to determine the modules involved with a merge.

    Overall, \tool assists users determine which modules are involved
    with a merge more quickly and accurately.

@@

\tool is able to assist users with summarizing various aspects of a
merge more quickly and accurately than Gitk. In two tasks, T5 and T9,
correctness was affected by the size of a tree, but in both trees, \tool
was able to provide a statistically significant improvement to the
correctness. Only in one task, T7, was timing affected by the size of a
tree; \tool did not significantly improve the time taken to answer T7 on
the smaller tree, but did improve the time taken on the larger tree.
